A sheaf--function dictionary for algebraic tori over local fields

### 2013-10-10 shanghai.tex
Edits to section 9

\begin{proposition}\label{prop:restriction}
For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf $\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$;
in particular, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
\end{proposition}

@@

 Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
 By Lemma~\ref{lemma:ext}, there is an extension of the 
 discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G^0$ 
 such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
 Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$ and 
 $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
\end{proof}

@@

\begin{proof}
Suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ 
and $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$.

@@

The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical 
in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$ 
then it follows from \ref{QC.2} and \ref{QC.3} 
that
 \begin{equation}\label{eq:qc}
  \begin{tikzcd}[column sep=60]
   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
  &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}  
  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'} 
  & {}
  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
  \end{tikzcd}
 \end{equation}
both commute.

Now, for each $x\in \pi_0(\bG)$, pick $g_x\in \bG^x$ 
and set $\gqcs{E}_x \ceq \gqcs{L}_{g_x}$. 
Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$ 
be the isomorphism of $\EE$-vector spaces obtained by composing 
$\varphi_{g_{\Frob{}(x)},\Frob{}(g_x)} : \gqcs{L}_{g_{\Frob{}(x)}} \to \gqcs{L}_{\Frob{}(g_x)}$ 
with $\phi_{g_x} : \gqcs{L}_{\Frob{}(g_x)} \to \gqcs{L}_{g_x}$. 
For each pair $x,y\in \pi_0(\bG)$ 
let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$ 
be the isomorphism of $\EE$-vector spaces obtained by composing
$\varphi_{g_{x+y},g_xg_y} : \gqcs{L}_{g_{x+y}} \to \gqcs{L}_{g_xg_y}$ 
with $\mu_{g_x,g_y} : \gqcs{L}_{g_xg_y} \to \gqcs{L}_{g_x}\otimes \gqcs{L}_{g_y}$.
Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
\begin{enumerate}
\item
the indexed set of one-dimensional $\EE$-vector spaces  $\gqcs{E}_x$, 
as $x$ runs over $\pi_0(\bG)$,
\item the indexed set of isomorphisms
  $\mu_{x,y} : \gqcs{E}_{x+y} \xrightarrow{\iso} \gqcs{E}_{x} \otimes\gqcs{E}_{y}$,
 as $x$ and $y$ run over $\pi_0(\bG)$,
 \item the indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$,
as $x$ runs over $\pi_0(\bG)$.
\end{enumerate}
We have now defined a quasicharacter sheaf $\qcs{E}$ on $\pi_0(G)$ 
from the quasicharacter sheaf $\qcs{L}$ on $G$ 
with the property $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$.

Now, pullback the quasicharacter sheaf $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$.
The resulting quasicharacter sheaf $\pi_0^* \qcs{E}$ is constant 
on geometric connected components, with stalks given by 
$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$; 
in particular, $\left(\pi_0^* \qcs{E}\right)\vert_{\bG^x} =  (\qcs{E}_{x})_{\bG^x}$.
Likewise, the quasicharacter sheaf $\qcs{L}$ is constant 
on geometric connected components. Our choices above define isomorphisms
$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$, for each $x\in \pi_0(\bG)$.
The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4}, 
thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$.

We have now show that if $\qcs{L}$ is a quasicharacter sheaf on $G$ and $\iota_0^*\qcs{L}= (\EE)_{G^0}$ then there is some quasicharacter sheaf $\qcs{E}$ on $\pi_0(G)$ such that $\qcs{L} \iso \pi_0^* \qcs{E}$. On the other hand, $\iota_0^*(\pi_0^* \qcs{E}) \iso (\EE)_{G^0}$, by Proposition~\ref{prop:pullback}. This shows that \eqref{eq:pi2} is exact at $\QC(G)$, concluding the proof of Proposition~\ref{prop:middleexact}.
\end{proof}

>>>>

\begin{proposition}\label{prop:restriction}
For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
\end{proposition}

@@

 Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
 By Lemma~\ref{lemma:ext}, there is an extension of the 
 discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G$ 
 such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
 Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$ and 
 $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
\end{proof}

@@

\begin{proof}
First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ 
with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.

@@

The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical 
in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$ 
then it follows from \ref{QC.2} and \ref{QC.3} 
that
 \begin{equation}\label{eq:qc}
  \begin{tikzcd}[column sep=55]
   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
  &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}  
  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'} 
  & {}
  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
  \end{tikzcd}
 \end{equation}
both commute.

For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$ 
and set $\gqcs{E}_x \ceq \gqcs{L}_{g(x)}$. 
Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$ 
be the isomorphism of $\EE$-vector spaces obtained by composing 
$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gqcs{L}_{g(\Frob{}(x))} \to \gqcs{L}_{\Frob{}(g(x))}$ 
with $\phi_{g(x)} : \gqcs{L}_{\Frob{}(g(x))} \to \gqcs{L}_{g(x)}$. 
For each pair $x,y\in \pi_0(\bG)$ 
let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$ 
be the isomorphism of $\EE$-vector spaces obtained by composing
$\varphi_{g(x+y),g(x)g(y)} : \gqcs{L}_{g(x+y)} \to \gqcs{L}_{g(x)g(y)}$ 
with $\mu_{g(x),g(y)} : \gqcs{L}_{g(x)g(y)} \to \gqcs{L}_{g(x)}\otimes \gqcs{L}_{g(y)}$.
Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.

The pullback $\pi_0^*(\qcs{E})$ of $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant 
on geometric connected components, with stalks given by 
$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\qcs{E}$ and $\qcs{L}$
are constant on geometric connected components of $G$. 
The choices above define isomorphisms
$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4}, 
thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$.
\end{proof}

To close this section, we note that the injectivity of $\pi_0^*$ will be proven in Corollary~\ref{cor:exact}.
